Genome-wide changes in expression during inflorescence architecture development

### 2015-07-30 ms.Rmd
run DESeq2 script

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
output:
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

@@

To recover common expression patterns in the meristem samples, read counts were transformed using the variance-stabilizing transformation (VST) included in the `DESeq2` package [@Love:2014cf], and the standardised, VST-transformed read counts were clustered using the fuzzy *c*-means algorithm implemented in the `Mfuzz` package [@Futschik:2005vo]. To determine the optimum number of clusters (*c*), the minimum distance between cluster centroids of clusters produced with *c* values between `cmin` to `cmax`,

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
output:
  pdf_document:
    fig_caption: yes
    keep_md: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

To recover common expression patterns in the meristem samples, read counts were transformed using the variance-stabilizing transformation (VST) included in the `DESeq2` package [@Love:2014do], and the standardised, VST-transformed read counts were clustered using the fuzzy *c*-means algorithm implemented in the `Mfuzz` package [@Futschik:2005vo]. To determine the number of cluster cores (*c*), the minimum distance between cluster centroids, the formation of empty clusters, and PCA plots of cluster members were monitored for clusters produced with *c* values between `cmin` and `cmax` (@SI). A cluster number of `{r} c` was chosen,
